
\documentclass[11pt]{article}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[textwidth=12cm,centering]{geometry}
\usepackage[x11names]{xcolor}
\usepackage{background}

\newcommand*\wb[3]{%
  {\fontsize{#1}{#2}\usefont{U}{webo}{xl}{n}#3}}

% The page frame
\SetBgColor{Goldenrod3}
\SetBgAngle{0}
\SetBgScale{1}
\SetBgOpacity{1}
\SetBgContents{%
\begin{tikzpicture}
\node at (0.5\paperwidth,0) {\wb{80}{34}{E}\rule[60pt]{.2\textwidth}{0.4pt}%
  \raisebox{55pt}{%
  \makebox[.6\textwidth]{\ \fontsize{24}{29}\selectfont\scshape Strom \& Katy }}%
  \rule[60pt]{.2\textwidth}{0.4pt}\wb{80}{34}{F}};
\node at (2,-0.5\textheight) {\rule{0.4pt}{.8\textheight}};
\node at (19.5,-0.5\textheight) {\rule{0.4pt}{.8\textheight}};
\node at (0.5\paperwidth,-\textheight) {\wb{80}{34}{G}\rule[-10pt]{\textwidth}{0.4pt}\wb{80}{34}{H}} ;
\end{tikzpicture}%
}

% colorize text
\newcommand*\ColText[1]{\textcolor{Goldenrod3}{#1}}

% a tabular* for each food group
%\newenvironment{Group}[1]
%  {\noindent\begin{tabular*}{\textwidth}{@{}p{.8\linewidth}@{\extracolsep{\fill}}r@{}}
%    {\fontsize{24}{29}\selectfont\ColText{#1}}\\[0.8em]}
%  {\end{tabular*}}

% a tabular* for each heading
\newcommand*\heading[2]{%
    \vspace{2.0em}
    {\fontsize{24}{29}\selectfont\ColText{#1}}\\
    {\fontsize{14}{14}\selectfont\ColText{(#2)}}\\\vspace{2.0em}}


\begin{document}
\begin{center}
\heading{Processional}{Wedding Party}
Greta Qaiyum\\
Allison Gouch\\
Peter Borman\\
Katy \& Strom

\heading{Welcome}{Greta}
Her own words.

\pagebreak
\heading{Kahlil Gibran - On Marriage}{Allison}
You were born together, and together you shall be forevermore.\\
You shall be together when the white wings of death scatter your days.\\
But let there be spaces in your togetherness,\\
And let the winds of the heavens dance between you.\\
\vspace{2mm}
Love one another, but make not a bond of love:\\
Let it rather be a moving sea between the shores of your souls.\\
Fill each other's cup but drink not from one cup.\\
Give one another of your bread but eat not from the same loaf\\
Sing and dance together and be joyous, but let each one of you be alone,\\
Even as the strings of a lute are alone though they quiver with the same music.\\
\vspace{2mm}
Give your hearts, but not into each other's keeping.\\
For only the hand of Life can contain your hearts.\\
And stand together yet not too near together:\\
For the pillars of the temple stand apart,\\
And the oak tree and the cypress grow not in each other's shadow.\\

\pagebreak
\heading{(Jalal ad-Din) Rumi - A Blessing}{Peter}
May these vows and this marriage be blessed.\\
May it be sweet milk,\\
this marriage, like wine and halvah.\\
May this marriage offer fruit and shade, like the date palm.\\
May this marriage be full of laughter,\\
your every day a paradise.\\
May this marriage be a sign of compassion,\\
a seal of happiness here and hereafter.\\
May this marriage have a fair face and a good name,\\
an omen as welcome\\
as the moon in a clear blue sky.\\

\pagebreak
\heading{Hopes}{Katy \& Strom}

Katy says some nice things to Strom.\\
Strom says some nice things to Katy.

\heading{Personal Vows}{Greta}

\begin{itemize}
\item[\textbf{Do you}] vow to support and nurture each other’s goals and dreams as if they were your own? (we do)
\item[\textbf{Do you}] vow to work to stay connected even when you change and grow individually? (we do)
\item[\textbf{Do you}] vow to take each other seriously when needed and to laugh together the rest of the time? (we do)
\item[\textbf{Do you}] vow to show every day that you adore and love each other? (we do)
\end{itemize}

\heading{Community Vow}{Greta}

Do you, the community around Katy and Strom, promise to encourage and love 
these two people, give them your guidance, and support them in the promises 
that they have made? (We Do) 

\pagebreak 
\heading{Ring Exchange}{Greta}

\textbf{Katy's ring} is no ordinary band. It was worn by Katy’s 
great-grandmother and namesake, Kathryn L. Crowe, on the event of her first 
wedding to Katy’s great-grandfather, Robert J. Donovan, 91 years ago. With this 
piece of family history, Katy and Strom celebrate the joining of their 
families.

\vspace{5mm}

\textbf{Strom's ring}, a golden band with a half twist in it, is also no ordinary ring. 
This M{\"o}bius Strip is a three-dimensional geometrical object with only one 
continuous surface and one continuous edge. With this symbol of oneness, Katy 
and Strom celebrate 
their union.

\newpage

Fin.
\end{center}
\end{document}

